---
title: "Testing Mock Jury"
output: pdf_document
date: "Wednesday, January 14, 2015"
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE, 
               message = FALSE, 
               warning = FALSE, 
               tidy = FALSE, 
               fig.align = "center", 
               fig.width = 5, 
               fig.height = 4, 
               fig.pos = "H", 
               cache = F)
set.seed(19)
```

## Comparing the Observed Mock Jury Data

```{r data}
library(heplots)
library(dplyr)
library(mosaic)
data(MockJury)
m1 <- MockJury %>% 
  select(Attr, Years) %>% 
  filter(Attr != "Beautiful") %>% 
  droplevels()
```

```{r beanplot}
library(beanplot)
par(mfrow = c(1,1))
beanplot(Years ~ Attr, data = m1, log = "", col = "bisque", method = "jitter", ylab = "Years")
```

## Looking at the Data

```{r print-data}
# knitr::kable(rbind(head(m1), tail(m1)), format = "markdown")
```
|   |Attr         |Years |
|:--|:------------|:-----|
|1  |Unattractive |1  |
|2  |Unattractive |4  |
|3  |Unattractive |3  |
|4  |Unattractive |2  |
|5  |Unattractive |8  |
|6  |Unattractive |8  |
|...|...          |...|
|70 |Average      |3  |
|71 |Average      |2  |
|72 |Average      |7  |
|73 |Average      |6  |
|74 |Average      |12 |
|75 |Average      |8  |

## Permuting the Data

```{r permute-data}
m1$perm_Attr <- shuffle(m1$Attr)
# knitr::kable(rbind(head(m1), tail(m1)), format = "markdown")
```

|   |Attr         | Years|perm_Attr    |
|:--|:------------|:-----|:------------|
|1  |Unattractive |     1|Average      |
|2  |Unattractive |     4|Unattractive |
|3  |Unattractive |     3|Unattractive |
|4  |Unattractive |     2|Average      |
|5  |Unattractive |     8|Unattractive |
|6  |Unattractive |     8|Average      |
|...|...          |...   | ...         |
|70 |Average      |     3|Unattractive |
|71 |Average      |     2|Average      |
|72 |Average      |     7|Average      |
|73 |Average      |     6|Average      |
|74 |Average      |    12|Unattractive |
|75 |Average      |     8|Unattractive |

## Comparing Averages

In the observed data, the unattractive women are given sentences that are `r round(diffmean(Years ~ Attr, data = m1), 2)` years longer than the unattractive women.

In the permuted data, the difference is only `r round(diffmean(Years ~ perm_Attr, data = m1), 2)` years.

## Null Distribution of Sentence Lengths

```{r null-distn, fig.width=5.5}
B <- 500
null <- rep(NA, B)
for(i in 1:B) {
  null[i] <- diffmean(Years ~ shuffle(Attr), data = m1)
}
hist(null, xlab = "Difference in Sentence Lengths", main = "Null Distribution of Sentence Lengths")
```

```{r p-value, fig.width=5.5}
hist(null, xlab = "Difference in Sentence Lengths", main = "Comparing Observed Difference to Null Distribution")
abline(v = 1.84, col = "red", lwd = 3)
```











